---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HIEdroughtbox

<!-- badges: start -->
<!-- badges: end -->

The goal of HIEdroughtbox is to facilitate the pre-prepossessing of the data 
produced by [droughtbox located at the Hawkesbury Institute for the Environment](https://ecamo19.github.io/droughtbox_documentation/) and prepare 
it for calculating the branch minimum conductance $g_{res}$ and it's temperature  
dependence $T_p$. 

Each dataset generated by the droughtbox have the following issues:

+    __The data file have a .dat extension with the first three rows of the 
     data file containing information about the variable measured, the units 
     and the type of data__. This which generates some errors when loaded into R 
     with the function read.table(). Thus, the `read_hie_droughtbox_data()` 
     function was developed for taking into account these issues.
     
    
+    __Contains data points outside of the time or dates desired.__ This 
     happens because the data logger collects all data, which might include 
     (among others) data generated by another person in a different day, 
     data generated during an undesired hour or data where the droughtbox didn't
     achieved the climatic conditions desired(i.e Temperature). Because of 
     these issues, the function `filter_droughtbox_data()` was developed. With 
     this function a date or hour (or both) interval can be chosen to focus on 
     a specific time period.

+    __Produce values close to zero (or even negative) and the firsts and last 
     data points within each taring process are not valid.__ Every 60 minutes 
     the droughtbox automatically tares itself to avoid drift in the 
     measurements. However this causes that between each taring process the 
     droughtbox records wrong data points. To overcome these issues the function
     `clean_droughtbox_data()` was developed. This function removes all values 
     below a desired threshold (the default is 0.2 grams) __AND__ the first and 
     last values within each taring process. For example 
     remove_n_observations = 10, removes the first 10 and last 10 values 
     within each taring process).
     
## Installation

You can install the development version of HIEdroughtbox from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("ecamo19/HIEdroughtbox")
```

## Data preprocessing example

```{r libraries, message = FALSE,warning = FALSE}
library(HIEdroughtbox)
library(dplyr)
```

### Read droughtbox data

The first step is reading the data. The `read_hie_droughtbox_data()` only reads
files with the .dat extension that haven't been modified. Thus make sure to 
provide __UNMODIFIED__ files coming from the droughtbox.  

```{r example}
droughtbox_data <- read_hie_droughtbox_data("inst/extdata/acacia_aneura_25c.dat")
glimpse(droughtbox_data)
```

### Visualize climatic conditions

The droughtbox have sensors that measures the temperature and the relative 
humidity. To visualize the set and measured climatic controls the followiong 
function can be used: 

```{r example_plot_climatic_controls, fig.height=20, fig.width=25}
plot_droughtbox_climatic_controls(droughtbox_data, cowplot = T)
```

### Visualize all weights measured by the droughtbox

With the function `plot_strains_weights` it is possible to visualize all weights 
measured by each strain inside the droughtbox. Also it let you identify to which
taring group does each data point belongs to (denoted as numbers).

```{r example_plot_raw_weights, fig.height=10, fig.width=15}
plot_strains_weights(droughtbox_data, 
                     show_strain = "all",
                     time_breaks = "5 min",
                     show_tare_group = TRUE)
```

... or just some strains 

```{r example_plot_raw_weights_1_4, fig.height=10, fig.width=15, warning=FALSE}
plot_strains_weights(droughtbox_data, 
                     show_strain =  "strain_4", 
                     time_breaks = "2 min",
                     show_tare_group = TRUE)
```

### Choose a interval of time

Using the previous plot as reference, I decided to focus only on the data 
collected between 13:10:00 and 15:10:00. 

```{r warning=FALSE, message=FALSE}
filtered_droughtbox_data <- filter_droughtbox_data(droughtbox_data, 
                       from_start_time = "13:10:00",
                       to_end_time = "15:10:00")

glimpse(filtered_droughtbox_data)
```



```{r example_plot_weights_1_4_filtered_data, fig.height=10, fig.width=15, warning=FALSE}
plot_strains_weights(filtered_droughtbox_data, 
                     show_strain = c("strain_1", "strain_4"), 
                     time_breaks = "10 min",
                     show_tare_group = TRUE)
```

### Clean the data

Finally, after filtering the data by the interval of time desired the last 
step is to remove the values close to zero and the first and last points within 
each taring process. 

The following code will remove the values lower than 0.2 grams and the first 10 
and last 10 values of each taring group.  

```{r}
clean_droughtbox_data <- 
    clean_droughtbox_data(filtered_droughtbox_data, 
                      remove_n_observations = 10, 
                      threshold = 0.2)

glimpse(clean_droughtbox_data)
```


```{r example_plot_weights_all_cleaned_data, fig.height=10, fig.width=15}
plot_strains_weights(clean_droughtbox_data, 
                     show_strain = "all",
                     time_breaks = "15 min",
                     # If true, this will display the taring group
                     show_tare_group = FALSE)
```

